\section{STRUCTURE AND ORGANISATION}

\item \textbf{Bodies} \\
DAA's bodies are the:
\begin{itemize}
    \item DAA Ballot Vote ("Urabstimmung");
    \item DAA Delegate ("Vorstand");
    \item DAA Member Community;
    \item DAA Whitelisters
\end{itemize}

\item \textbf{General Concept of Competences and Duties} \\
The objective of DAA is to establish a decentralised and democratic association with flat hierarchies.
Therefore, the DAA Delegate (“Vorstand”) will have only those competences, which actually require the action of an individual, natural person, such as representation duties or the duty to keep the books.
The DAA Ballot Vote ("Urabstimmung") has those elementary competences, which are mandatory stipulated for an association assembly by Swiss law (such as the change of statutes, the liquidation of the association, and others).
The DAA Ballot Vote will be held digital, allowing the proper democratic decision-making required by Swiss law.
Thirdly, the DAA Member Community shall be the body, which can decide about the "daily business" such as the proposal and support of projects and the funding allocation to projects.
Every member of the association is also part of the DAA Member Community, which provides a blockchain-based technical infrastructure to efficiently, democratically and transparently propose and vote.
See Visualisation in Annex?????

\item \textbf{Underlying Technology} \\
The DAA is technically built on an Ethereum-based Smart Contract System (SCS).
All voting will take place on this technical infrastructure.
The relevant technical functions are hereinafter written in red/italic.
To be able to vote, holding a certain amount of Ether is necessary for every member (transaction fees, gas fees).

\item \textbf{DAA Delegate (Vorstand)} \\
The DAA has one (1) Delegate with the following competencies and duties:
\begin{enumerate}
    [label=(\alph*)]
    \item Representing the DAA to the outside world;
    \item Keeping the books and creating the necessary financial statements of the DAA;
    \item Preparing and calling the next DAA Ballot Vote (\textcolor{red}{\emph{setVotingSlot}});
    \item Regulating signatory powers;
    \item Adding and removing member whitelisters (\textcolor{red}{\emph{addWhitelisters}} \& \textcolor{red}{\emph{removeWhitelisters}});
    \item Remove Members who haven't paid their membership fees;
    \item Appointing the informal DAA Board of Advisors; %TODO
    \item Keeping the member registry (name, address, e-mail) together with the DAA whitelisters. %TODO
\end{enumerate}
The term of office for the DAA Delegate starts with the foundation of this DAA and ends when he's been replaced via a proposal.
If the DAA delegate becomes unable to act or loses his private key, an extraordinary DAA Ballot Vote will be called and a new DAA Delegate elected.
The personal liability of the DAA Delegate is limited to cases of gross negligence.

\item \textbf{DAA Ballot Vote ("Urabstimmung")} \\
\begin{enumerate}[label=\textbf{\arabic*.}]
    \item \textbf{Competences} \\
    The DAA Ballot Vote shall be the highest governing body of the DAA.
    It is chaired by the DAA Delegate or, when the Delegate is unavailable, by another member appointed by the Assembly.
    The DAA Ballot Vote has the duty of collecting all the votes on the proposals on that vote.

    \item \textbf{Voting Majorities} \\
    Resolutions shall be adopted by a simple majority of the members participating at the individual DAA Ballot Vote.
    At least 1/5 of the DAA Member Community must vote on a proposal to become successful.
    The update of the underlying code (lit. g ???) and the dissolution of the DAA (lit. e.????) require a majority of 2/3 of the DAA Member Community. %TODO
    The DAA Member Community has a one day timeslot to vote for every proposal in the Ballot Vote.

    \item \textbf{Election Process for DAA Delegate} \\
    % TODO: Delegate election
    Any member can propose himself for candidacy as delegate (proposeDelegateCandidancy).
    Any member can vote for exactly one candidate (VoteForDelegate) or not vote at all.
    The candidate with most votes in favour will be the new DAA Delegate, beginning at the end of the DAA Assembly.
    If two or more candidates have the same (and the most) number of votes, a new election on only those candidates will take place.

    \item \textbf{Convocation} \\
    The DAA Ballot Vote shall be held in regular intervals.
    The DAA Delegate can set the date at least 1 month before the DAA Assembly (\textcolor{red}{\emph{setVotingSlot}}).
    The DAA Delegate will inform the members electronically on the place and date.
    A DAA Ballot Vote lasts one full day. \\ \\ %TODO

    Every member can propose an extraordinary DAA Assembly (proposeGeneralAssemblyDate). %TODO
    The time slot for the vote (voteForGeneralAssemblyDate) is two weeks.
    If 20\% of all DAA members support the extraordinary DAA Assembly, it will take place on the specified date.
    If the DAA Delegate is voting on behalf of the extraordinary DAA Assembly, it will take place irrespective of any majority or quorum. \\ \\
    The DAA Ballot Vote is held purely digital.

    \item \textbf{Motions \& Agenda Items} \\ %TODO
    Motions from members must be submitted at least 7 days prior to the DAA Assembly using the specific DAO proposal function.
    Other matters can only be discussed with the consent of the DAA Delegate.
\end{enumerate}


\item \textbf{DAA Member Community} \\
\begin{enumerate}[label=\textbf{\arabic*.}]
    \item \textbf{Members \& Purpose} \\
    Every member of the DAA is also member of the DAA Member Community.
    The objective of the DAA Member Community is to allow every member to permanently propose new DAA projects and to vote on the funding allocation to those projects. %TODO
    In this area, the DAA Member Community is the executive body of the DAA.
    The funding allocation via the DAA Member Community voting mechanism is binding and technically non-reversible – not even by the DAA Delegate or the DAA Ballot Vote.

    \item \textbf{Competences} \\
    The DAA Member Community has the following competences:
    \begin{enumerate}
        [label=(\alph*)]
        \item Proposing new projects and funding allocations (\textcolor{red}{\emph{propose}});
        \item Voting on those projects and the use of funds (\textcolor{red}{\emph{castVote}} or \textcolor{red}{\emph{castVoteWithReason}});
        \item Expelling DAA members (see Art. 17).
    \end{enumerate}

    \item \textbf{Proposal \& Voting Process} \\
    The whole voting process on the DAA Member Community is purely digital and block- chain-based.
    Every member can submit a proposal to pay Ether to a destination address (the amount can be zero). %TODO
    The proposals must be readable by an external Smart Contract so that they can act on an outcome (e.g. external sponsor backs project if a majority is in favour of a project). %TODO
    The votes require simple majority and a 1/5 quorum of the DAA Member Community.
    The time slot for a proposal vote is one day during the DAA Ballot Vote.
\end{enumerate}

\item \textbf{DAA Whitelisters} \\
The DAA Whitelisters review member applicants on their eligibility to join the DAA.
If the member meets the requirements of Art. 11, the DAA Whitelisters will add their public keys to the member registry (\textcolor{red}{\emph{whitelistMember}}).
The DAA Whitelisters are be appointed and removed by the DAA Delegate (\textcolor{red}{\emph{addWhitelisters}} \& \textcolor{red}{\emph{removeWhitelister}}).
The minimum amount of DAA Whitelisters is two (2).
